\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
fixed 2 graphs per suggestion and thickened lines
tweaks to abstract, intro, and sect 5 up till agent behaviors

\usepackage[pdftex]{graphicx}
\usepackage{subfig}
% TODO remember we need to meet color compliance:
% http://its.papercept.net/conferences/support/general.php

% TODO better name!
\title{\LARGE \bf
Approximately Orchestrated Road Traffic Automata:\\
Large-scale Traffic Simulation for Autonomous Vehicles
}

@@

Autonomous vehicles have seen great advancements in recent years, and such
vehicles are now ever closer to being commercially available.  The advent of
driverless cars provides opportunities for optimizing traffic in ways not
possible before. This paper introduces an open source multiagent microscopic
traffic simulator called AORTA, which stands for \textit{Approximately
Orchestrated Road Traffic Automata}, designed for optimizing autonomous traffic
at a city-wide scale. AORTA creates scale simulations of the real world by
generating maps using publicly available road data from \textit{OpenStreetMap}
(OSM). This allows simulations to be set up through AORTA for a desired region
anywhere in the world in a matter of minutes. AORTA allows for optimizing
traffic by creating more intelligent behaviors for individual drivers (agents),
as well as by defining new intersection policies that can be followed by these
autonomous agents. These agent behaviors define how agents interact with one
another, follow intersection policies, and select the next action to take. This
paper demonstrates a simple applications using AORTA through an experiment
testing an intersection policy designed for autonomous vehicles at a city-wide
scale.

@@

% theme: easy simulation in your city, in 2 minutes!
% be sure to emphasize open source!
% contribution: autonomous car / human car sim on EXISTING INFRASTRUCTURE

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2004, the farthest distance traveled by a vehicle autonomously in the DARPA
Grand Challenge was 11.9km \cite{cnnGrandChallenge2004}. By 2007, six of the
competing teams completed the 96km course set for the DARPA Urban Challenge
\cite{spectrumUrbanChallenge2007}. They did so while following the same traffic
laws followed by human drivers, navigating along with other moving vehicles,
and following correct intersection precedence order. Since then, Google's
driverless cars have clocked more than 250,000km on public roads in urban
California, USA \cite{tedThrun2011}. In 2010, researchers from the University
of Parma successfully completed an autonomous \textit{intercontinental} run
from Parma, Italy to Shanghai, China \cite{cnnVislab2010}. The successful
completion of all these milestones suggests that autonomous cars are here to
stay, and are ever closer to becoming commercially available. With the arrival
of autonomous cars, it also becomes possible to optimize traffic in ways not
possible for human drivers. 
\commentd{If we need space, I agree with Dr Chiu, some of this could be trimmed}

@@

This paper introduces an open source multigent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Road Traffic
Automata}, a platform designed for testing autonomous vehicle behaviors and
intersection policies. Autonomous vehicles, termed agents, use
behaviors to interact with one another, follow intersection policies, and
decide on both long term and short term actions. AORTA allows for the creation
of intersection policies that designate when agents can cross the
intersection. AORTA's goal is to allow for the definition of new agent
behaviors and intersection policies to optimize autonomous traffic.
Additionally, by assigning human-like behaviors such as the ``car following
model'' \cite{brackstone1999car} to agents, and traffic-signal-like policies to
intersections, AORTA could potentially simulate human traffic.
\commentd{Previously, ``AORTA allows for the creation
of intersection policies on top of a reservation based intersection manager
\cite{JAIR08-dresner}, and these policies designate when agents can cross the
intersection.'' Actually, reservations are just one policy. Do we want to focus
on the general case here, or autonomous specifically?}

@@

\commentd{Is this incomplete?}
Different elements of the simulator are described as follows:

@@

% \textit{dt}.
% This lets agents reason about how far they will travel for a given choice of
% acceleration before being able to choose a different acceleration. Setting
% \textit{dt} to the ``reaction time'' of a human driver may be appropriate for
% experiments modeling humans.
% 
% Each step, the simulation does the following:

@@

\commentpk{need to check the ordering of above enumeration}

@@

Every step, a generator creates some number of new agents. If the agent's route
policy needs computation like pathfinding to operate, the generator either
performs it immediately (incurring a delay in simulation if it is running) or,
if possible, sends it to a pool of worker threads to process in the background.
Once an agent's route is ready, the agent waits alongside its starting lane (as
if it is in a driveway or parking lot). When the lane has no agents that could
potentially crash with the new vehicle, the new agent enters the system. % with
%zero initial speed. Because behaviors must enforce speed limit along a lane
%from the moment an agent enters a road, it is safe for a new agent to enter a
%road if there is no other agent within the worst-case distance (traveling
%distance at the speed limit, plus stopping distance from this speed) preceeding
%the spawn point. To avoid predicting which agents might enter the lane in the
%near future, there is a buffer space at the beginning of the lane where a new
%agent may never spawn. This disqualifies some short lanes from being spawn
%points, but this is not a big limitation in practice. \commentpk{I understand
%your concern about explaining the entire methodology, but the last 2 lines are
%unnecessary and somewhat distracting}

@@

All traversables (lanes and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. A collision is detected when two agents
reverse order after a time step has completed.

Intersections check for collisions by examining the turn each agent is
performing and verifying that no other agent is simultaneously performing a
conflicting turn. AORTA has a low-granularity model of turn conflict. If two
vehicles at any point along two different turns could ever come into contact,
then the turns are always in conflict, no matter where the agents actually are
along that turn. This is visualized in figure \ref{fig:conflicts}. Further work
is required before higher granularity can be introduced through space-time
tiling intersections \cite{JAIR08-dresner}, due to some of the complex
intersection geometries inferred from OSM. An example of such a difficult
intersection is shown in figure \ref{fig:crazyIntersection}.

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{avg_lag_agent_atx.png}
  \caption{The distribution of average delay reveals that traffic signals can
           cause the most lag.}
  \label{fig:avg_lag}
  \vspace{-10pt}
\end{figure}
\commentc{This figure only shows the distributions for a particular
  traffic level only. People would wonder what is the traffic level.
Actually people are more interested to see how it varies with
different traffic levels so a few more graphs like this at
different traffic level is helpful.}
\commentc{Remove ``In this range'' in the y-label.}
\commentc{Replace ``lag'' with ``delay'' in the x-label}

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{agent_cnt_atx.png}
  \caption{Autonomous reservations outperform stop signs, and traffic signal
           gridlocked. \commentc{This label is not helpful. Clarify ``active'' in y label.}}
  \label{fig:agent_cnt}
  \vspace{-10pt}
\end{figure}

>>>>

\usepackage[pdftex]{graphicx}
\usepackage[font={footnotesize}]{caption,subfig}
% TODO remember we need to meet color compliance:
% http://its.papercept.net/conferences/support/general.php

% TODO better name!
\title{\LARGE \bf
Approximately Orchestrated Routing and Transportation Analyzer:\\
Large-scale Traffic Simulation for Autonomous Vehicles
}

@@

Autonomous vehicles have seen great advancements in recent years, and such
vehicles are now ever closer to being commercially available. The advent of
driverless cars provides opportunities for optimizing traffic in ways not
possible before. This paper introduces an open source multiagent microscopic
traffic simulator called AORTA, which stands for \textit{Approximately
Orchestrated Routing and Transportation Analyzer}, designed for optimizing
autonomous traffic at a city-wide scale. AORTA creates scale simulations of the
real world by generating maps using publicly available road data from
\textit{OpenStreetMap} (OSM). This allows simulations to be set up through AORTA
for a desired region anywhere in the world in a matter of minutes. AORTA allows
for traffic optimization by creating intelligent behaviors for individual driver
agents and intersection policies to be followed by these agents. These behaviors
and policies define how agents interact with one another, control when they
cross intersections, and route agents to their destination. This paper
demonstrates a simple application using AORTA through an experiment testing an
intersection policy designed for autonomous vehicles at a city-wide scale.

@@

% TODO theme: easy simulation in your city, in 2 minutes!

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2004, the farthest distance traveled by a vehicle autonomously in the DARPA
Grand Challenge was 11.9km \cite{cnnGrandChallenge2004}. By 2007, six of the
competing teams completed the 96km course set for the DARPA Urban Challenge
\cite{spectrumUrbanChallenge2007}. They did so while obeying the traffic laws
followed by human drivers, navigating along with other moving vehicles, and
following correct intersection precedence order. Since then, Google's driverless
cars have clocked more than 250,000km on public roads in urban California, USA
\cite{tedThrun2011}. In 2010, researchers from the University of Parma
successfully completed an autonomous \textit{intercontinental} run from Parma,
Italy to Shanghai, China \cite{cnnVislab2010}. The successful completion of all
these milestones suggests that autonomous cars are here to stay, and are ever
closer to becoming commercially available. With the arrival of autonomous cars,
it also becomes possible to optimize traffic in ways not possible for human
drivers. 
%\commentd{If we need space, I agree with Dr Chiu, some of this could be trimmed}

@@

This paper introduces an open source multigent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Routing and
Transportation Analyzer}, a platform designed for testing autonomous vehicle
behaviors and intersection policies. Autonomous vehicles, termed agents, use
behaviors to interact with one another, follow intersection policies, and decide
on both long term and short term actions. AORTA allows for the creation of
intersection policies that designate when agents can cross the intersection.
AORTA's goal is to allow for the definition of new agent behaviors and
intersection policies to optimize autonomous traffic.  Additionally, by
assigning human-like behaviors such as the ``car following model''
\cite{brackstone1999car} to agents, and traffic-signal-like policies to
intersections, AORTA could potentially simulate human traffic.
\commentd{Previously, ``AORTA allows for the creation of intersection policies
  on top of a reservation based intersection manager \cite{JAIR08-dresner}, and
  these policies designate when agents can cross the intersection.'' Actually,
  reservations are just one policy. Do we want to focus on the general case
here, or autonomous specifically?}

@@

This section describes the simulator's agent model and its mechanisms for
creating agents, verifying safety, and allowing agents and intersections to
control themselves. Comments on current limitations and how to extend the
simulator follow.

@@

@@

@@

Every step, a generator creates some number of new agents. The generator either
immediately performs any timely computation required by the agent's route
policy, such as pathfinding, or delegates it to a pool of worker threads to
process in the background.  Once an agent's route is ready, the agent waits
alongside its starting lane (as if it is in a driveway or parking lot). When the
lane has no agents that could potentially crash with the new vehicle, the new
agent enters the system.
%with zero initial speed. Because behaviors must enforce speed limit along a lane
%from the moment an agent enters a road, it is safe for a new agent to enter a
%road if there is no other agent within the worst-case distance (traveling
%distance at the speed limit, plus stopping distance from this speed) preceeding
%the spawn point. To avoid predicting which agents might enter the lane in the
%near future, there is a buffer space at the beginning of the lane where a new
%agent may never spawn. This disqualifies some short lanes from being spawn
%points, but this is not a big limitation in practice. \commentpk{I understand
%your concern about explaining the entire methodology, but the last 2 lines are
%unnecessary and somewhat distracting}

@@

All traversables (lanes and turns) maintain an ordered queue of occupying
agents. A collision is detected when two agents reverse order after a time step
has completed.

Intersections check for collisions by verifying no two agents are simultaenously
performing a conflicting turn. AORTA has a low-granularity model of turn
conflict. If two vehicles at any point along two different turns could ever come
into contact, then the turns are always in conflict, no matter where the agents
actually are along that turn. This is visualized in figure \ref{fig:conflicts}.
Further work is required before higher granularity can be introduced through
space-time tiling intersections \cite{JAIR08-dresner}, due to some of the
complex intersection geometries inferred from OSM. An example of such a complex
intersection is shown in figure \ref{fig:crazyIntersection}.

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{avg_lag_agent_atx.png}
  \caption{The distribution of average delay reveals that traffic signals can
           cause the most lag.}
  \label{fig:avg_lag}
  \vspace{-10pt}
\end{figure}
\commentc{This figure only shows the distributions for a particular
  traffic level only. People would wonder what is the traffic level.
Actually people are more interested to see how it varies with
different traffic levels so a few more graphs like this at
different traffic level is helpful.}

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{agent_cnt_atx.png}
  \caption{Autonomous reservations outperform stop signs, and traffic signal
           gridlocked.}
  \label{fig:agent_cnt}
  \vspace{-10pt}
\end{figure}
